---
title: "occupation_sort_and_filter"
author: "bus 355"
date: "10/4/2019"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(janitor)
library(tidyverse)

```

## Occupation Data, Sort and Filter

Load the data
```{r}
load("occupation_data.RData")

```

# Sorting and Filtering Questions

## Which are the 10 fastest growing occupations?
```{r echo=FALSE}
occupation %>%
  select(occ_title, emp_ch_per) %>%
  arrange(desc(emp_ch_per)) %>%
  head(10)
```


## Which are the 10 slowest growing occupations?
```{r echo=FALSE}
occupation %>%
  select(occ_title, emp_ch_per) %>%
  arrange(emp_ch_per) %>%
  head(10)

```

## Which are the 10 occupations with the highest number of employees?
```{recho=FALSE}
occupation %>%
  select(occ_title, emp_2018) %>%
  arrange(desc(emp_2018)) %>%
  head(11)

```

## Which are the 10 occupations with the highest self-employed percentage?
```{r}

```

## Which are the 10 highest paid occupations with a Master's degree?
```{r echo=FALSE}
occupation %>%
  select(occ_title, entry_edu, median_wage) %>%
  filter(entry_edu == "Bachelor's degree") %>%
  arrange(desc(median_wage)) %>%
  head(10)
```

## Which are the 10 highest paid occupations with a Doctoral degree?
```{r}

```

## Which are the 10 highest paid occupations with a High School degree?
```{r}

```

## Which are the 10 highest paid occupations with some college?
```{r}

```

## Which are the 10 highest paid occupations with a Bachelor's degree?
```{r}

```

## Which are the 10 highest paid occupations with a Bachelor's degree with NO work experience?
```{r}

```

