---
title: "occupation.Rmd"
author: "bus 355"
date: "10/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(janitor)
library(tidyverse)

```

## Occupation Data

Load the data
```{r}
load("occupation_data.RData")

```

Prep the variable names
```{r}
#clean variable names, via janitor package
names(occupation)
occupation <- clean_names(occupation)

# create a list of the variable names
occ_names <- names(occupation)

# see variable names
occ_names

# Can we change the first variable name?
occ_names[1] <- "occ_title"

# create a vector of names
occ_names_new <- c("occ_title","occ_code","occ_type","emp_2018","emp_2028",
                   "emp_ch_num","emp_ch_per","self_emp_per","occ_openings",
                   "median_wage","entry_edu","work_exp","otj_training")

# set names to the data
names(occupation) <- occ_names_new

# see variable names now
names(occupation)

```



# Which are the 10 fastest growing occupations?
```{r echo=FALSE}
occupation %>%
  select(occ_title, emp_ch_per) %>%
  arrange(desc(emp_ch_per)) %>%
  head(10)
```


# Which are the 10 slowest growing occupations?
```{r}

```

# Which are the 10 occupations with the highest number of employees?
```{r}

```

# Which are the 10 occupations with the highest self-employed percentage?
```{r}

```


# Which are the 10 highest paid occupations with a Master's degree?
```{r}

```


# Which are the 10 highest paid occupations with a Doctoral degree?
```{r}

```

# Which are the 10 highest paid occupations with a High School degree?
```{r}

```

# Which are the 10 highest paid occupations with some college?
```{r}

```

# Which are the 10 highest paid occupations with a Bachelor's degree?
```{r}

```

# Which are the 10 highest paid occupations with a Bachelor's degree with NO work experience?
```{r}

```


